Make any stupid plot you want

### 2021-01-28 draft/sections/math.tex
math

\paragraph{Example: Invalid Q}
\note{DEGENERATE Q - drawing a blank if this is necessry and if so how}
Check a well defined map $\monoid\times Y \rightarrow Y$.

@@

\subsubsection{Sample Qs}
%rewrite as alpha/beta 
In this section we formulate the minimal Q that will generate distinguishable graphical marks: non-overlapping scatter points, a non-infinitely thin line, and a simple heatmap.

\paragraph{Q: scatter plot}\mbox{} \\
\label{sec:artist_example_scatter}
\begin{figure}[H]
    \includegraphics[width=\textwidth]{figures/math/scatter.png}
    \label{fig:artist_scatter}
\end{figure}

\begin{equation}
Q(xpos, ypos)(\alpha_{1}, \alpha_{2}) 
\end{equation}

Given a defaut color of black, $\rho_{RGB} = (0,0,0)$. The position of this swatch of color can be computed relative to the location on the disc $S_{i}$ as shown in figure~\ref{fig:artist_scatter}:
\begin{align}
x &= size\bullet \alpha_1 \bullet \cos(\alpha_2) + xpos\\
y &= size\bullet \alpha_1 \bullet \sin(\alpha_2) + ypos
\end{align}

such that $\rho(s) = (x, y, 0, 0, 0)$ where $s$ is the region in $H$.

\paragraph{Q: line plot}\mbox{} \\
\label{sec:artist_example_line}
\begin{figure}[H]
    \includegraphics[width=\textwidth]{figures/math/line.png}
    \label{fig:artist_line}
\end{figure}

The line plot shown in fig~\ref{fig:artist_scatter} exemplifies the need for the jet discussed in section~\ref{sec:sheaf_stalk}
(needs the normal to push up/down against the normal)

\begin{equation}
    Q(xpos, \hat{n_{1}}, ypos, \hat{n_{2}})(\alpha_1, \alpha_2)
\end{equation}

where the magnitude of the thickness is 
\begin{equation}
    \lvert n \rvert = \sqrt{{n_{1}}^2 + {n_{2}}^2}
\end{equation}
such that the components are 
\begin{equation}
    \hat{n_{1}} = \frac{n_1}{\lvert n \rvert}, \; \hat{n_{2}} = \frac{n_2}{\lvert n \rvert}
\end{equation}

%% only alpha1 exists on the data side
which yields components of $\rho(s)$:
\begin{align}
 x = xpos(\xi(\alpha_1)) &+ \alpha_2\hat(n_1)(\xi(\alpha_1)) \\
 y = ypos(\xi(\alpha_1)) &+ \alpha_2\hat(n_2)(\xi(\alpha_2)) 
\end{align}

\paragraph{Q: heatmap}\mbox{} \\
\label{sec:artist_example_heatmap}
\begin{figure}[H]
    \includegraphics[width=\textwidth]{figures/math/heatmap.png}
    \label{fig:artist_heatmap}
\end{figure}
The heatmap in figure~\ref{fig:artist_heatmap} 
\begin{equation}
Q(xpos, ypos, color)
\end{equation}
has in the simple case a direct lookup into $K$ to obtain the $\mu = (x,y,c)$ values that are mapped into 
(arrays are upside down, x is y, is x) - $\xi$ is about translating indices from data to visual alignment
\begin{align}
D_{RGB} &= color(\xi(\alpha_1, \alpha_2))
D_x & = xpos(\xi(\alpha_1, \alpha_2))
D_y &= ypos(\xi(\alpha_1, \alpha_2))
\end{align}
through $\rho$.

>>>>

\note{DEGENERATE Q - drawing a blank if this is necessry and if so how\\
Check a well defined map $\monoid\times Y \rightarrow Y$}

@@

\subsubsection{Sample Qs}
%rewrite as alpha/beta 
In this section we formulate the minimal Q that will generate distinguishable graphical marks: non-overlapping scatter points, a non-infinitely thin line, and a heatmap. 
\label{sec:artist_example_scatter}
\begin{figure}[H]
    \includegraphics[width=\textwidth]{figures/math/scatter.png}
    \caption{The data is discrete points (temperature, time). Via \vchannel\ these are converted to (xpos, ypos) and pulled over discrete \gbase. These values are then used to parameterize \gsection which returns a color based on the parameters (xpos,ypos) and position $\alpha, \beta$ on $\gbase_{\dbasepoint}$ that \gsection\ is evaluated on. 
    }
    \label{fig:artist_scatter}
\end{figure}
The scatter plot in figure~\ref{fig:scatter} can be defined as $\vmark(xpos, ypos)(\alpha, \beta)$ where color $\gsection_{RGB} = (0,0,0)$ is defined as part of \vmark\ and $\gbasepoint=(\alpha, \beta)$ defines the region on \gbase. The position of this swatch of color can be computed relative to the location on the disc $\gbase_{\dbasepoint}$ as shown in figure~\ref{fig:artist_scatter}:
\begin{align}
x &= size\bullet \alpha \bullet \cos(\beta) + xpos\\
y &= size\bullet \alpha \bullet \sin(\beta) + ypos
\end{align}

such that $\gsection(\gbasepoint) = (x, y, 0, 0, 0)$ colors the point (x,y) black.

\label{sec:artist_example_line}
\begin{figure}[H]
    \includegraphics[width=\textwidth]{figures/math/line.png}
    \caption{The line fiber $(time,\, temp)$ is thickend with the derivative $(time^{\prime},\, temperature^{\prime}$ because that information will be necessary to figure out the tangent to the point to draw a thick line. This is because the line needs to be pushed perpendicular to the tangent of (xpos, ypos). \note{this is gonna move once this gets regenerated w/ labels} The data is converted to visual characteristics (xpos, ypos). The $\alpha$ coordinates on \gbase\ specifies the position of the line, the $\beta$ coordinate specifies thickness.}
    \label{fig:artist_line}
\end{figure}

The line plot $\vmark(xpos, \hat{n_{1}}, ypos, \hat{n_{2}})(\alpha, \beta)$ shown in fig~\ref{fig:artist_scatter} exemplifies the need for the jet discussed in section~\ref{sec:sheaf_stalk}. The line needs to know the tangent of the data to draw an envelope above and below each (xpos,ypos) such that the line appears to have a thickness. The magnitude of the thickness is 
\begin{equation}
    \lvert n \rvert = \sqrt{{n_{1}}^2 + {n_{2}}^2}
\end{equation}
such that the normal is  
\begin{equation}
    \hat{n_{1}} = \frac{n_1}{\lvert n \rvert}, \; \hat{n_{2}} = \frac{n_2}{\lvert n \rvert}
\end{equation}

which yields components of \gsection
\begin{align}
 x = xpos(\vindex(\alpha)) &+ \beta\hat(n_1)(\vindex(\alpha)) \\
 y = ypos(\vindex(\alpha)) &+ \beta\hat(n_2)(\vindex(\alpha)) 
\end{align}

where (x,y) look up the position $\vindex(\alpha)$ on the data and then apply thickness $\beta$ at that location.

\paragraph{Q: heatmap}\mbox{} \\
\label{sec:artist_example_heatmap}
\begin{figure}[H]
    \includegraphics[width=\textwidth]{figures/math/heatmap.png}
    \caption{The only visual parameter a heatmap requires is color since \vindex\ encodes the mapping between position in data and position in graphic. }
    \label{fig:artist_heatmap}
\end{figure}

The heatmap $\vmark(color)$ in figure~\ref{fig:artist_heatmap} is a direct lookup $\vindex:\gbase\rightarrow\dbase$ such that

\begin{align}
R &= R(\vindex(\alpha, \beta))\\
G &= G(\vindex(\alpha, \beta))\\
B &= B(\vindex(\alpha, \beta))
\end{align}
where \vindex\ may do some translating to a convention expected by \vmark\, for example reorientng the array such that the first row in the data is at the bottom of the graphic.
